\documentclass[12pt,openany,a4paper]{book}
\usepackage{graphicx}	% if you want encapsulated PS figures.
\usepackage{wrapfig}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage[skip=2pt]{caption} % Bring captions closer to figure

% Rename bibliography to reference
\usepackage[nottoc,notlof,notlot]{tocbibind} 
\renewcommand\bibname{References}

\usepackage{cite}

\graphicspath{{imgs/}}

% Number subsections but not subsubsections:
\setcounter{secnumdepth}{2}
% Show subsections but not subsubsections in table of contents:
\setcounter{tocdepth}{2}

\pagestyle{headings}		% Chapter on left page, Section on right.
\raggedbottom

\setlength{\topmargin}		{-5mm}  %  25-5 = 20mm
\setlength{\oddsidemargin}	{10mm}  % rhs page inner margin = 25+10mm
\setlength{\evensidemargin}	{0mm}   % lhs page outer margin = 25mm
\setlength{\textwidth}		{150mm} % 35 + 150 + 25 = 210mm
\setlength{\textheight}		{240mm} % 

\renewcommand{\baselinestretch}{1.2}	% Looks like 1.5 spacing.

% Stop figure/tables smaller than 3/4 page from appearing alone on a page:
\renewcommand{\textfraction}{0.25}
\renewcommand{\topfraction}{0.75}
\renewcommand{\bottomfraction}{0.75}
\renewcommand{\floatpagefraction}{0.75}

% AIDS TO CROSS-REFERENCING (All take a label as argument):
\newcommand{\eref}[1] {(\ref{#1})}		% (...)
\newcommand{\eq}[1]   {Eq.\,(\ref{#1})}		% Eq.~(...)
\newcommand{\eqs}[2]  {Eqs.~(\ref{#1}) and~(\ref{#2})}
\newcommand{\dfn}[1]  {Definition~\ref{#1}}	% Definition~...
\newcommand{\thrm}[1] {Theorem~\ref{#1}}	% Theorem~...
\newcommand{\lem}[1]  {Lemma~\ref{#1}}		% Lemma~...
\newcommand{\fig}[1]  {Fig.\,\ref{#1}}		% Fig.~...
\newcommand{\tab}[1]  {Table~\ref{#1}}		% Table~...
\newcommand{\chap}[1] {Chapter~\ref{#1}}	% Chapter~...
\newcommand{\secn}[1] {Section~\ref{#1}}	% Section~...
\newcommand{\ssec}[1] {Subsection~\ref{#1}}	% Subsection~...

% AIDS TO FORMATTING:
\newcommand{\teq}[1]	{\mbox{$#1$}}	% in-Text EQuation (unbreakable)
\newcommand{\qed}	{\hspace*{\fill}$\bullet$}	% end of proof

% MATHEMATICAL TEMPLATES:
% Text or math mode:

% ORDINAL NUMBERS:
\newcommand{\ith}	{\ensuremath{i^{\rm th}}}
\newcommand{\jth}	{\ensuremath{j^{\rm th}}}
\newcommand{\kth}	{\ensuremath{k^{\rm th}}}
\newcommand{\lth}	{\ensuremath{l^{\rm th}}}
\newcommand{\mth}	{\ensuremath{m^{\rm th}}}
\newcommand{\nth}	{\ensuremath{n^{\rm th}}}

% NB: These have not been tested since being modified for LaTeX2e.
\newcommand{\pack}	{\hspace{-0.08em}}
\newcommand{\Pack}	{\hspace{-0.12em}}
\newcommand{\Hz}	{\ensuremath{\rm\,H\pack z}}
\newcommand{\cm}	{\ensuremath{\rm\,cm}}
\newcommand{\s}		{\ensuremath{\rm\,s}}
\newcommand{\ms}	{\ensuremath{\rm\,m\pack s}}
\newcommand{\us}	{\ensuremath{\rm\,\mu s}}

\begin{document}

\frontmatter
% By default, frontmatter has Roman page-numbering (i,ii,...).

\begin{titlepage}
\renewcommand{\baselinestretch}{1.0}
\begin{center}
\vspace*{35mm}
\Huge\bf
		Analysing time-stepped \\
        nerual networks with temporally \\
        rich frame-based data \\
\vspace{20mm}
\large\sl
		by\\
		Joshua Arnold
		\medskip\\
\rm
		School of Information Technology and Electrical Engineering,\\
		The University of Queensland.\\
\vspace{30mm}
		Submitted for the degree of\\
		Bachelor of Engineering
		\smallskip\\
\normalsize
		in the field of Software Engineering
		\medskip\\
\large
		June 2016.		
\end{center}
\end{titlepage}

\cleardoublepage

\begin{flushright}
	ADDRESS LINE 1\\
	ADDRESS LINE 2\\
	Tel.\ (07) nnnn nnnn\\
	\medskip
	\today
\end{flushright}
\begin{flushleft}
  Prof Paul Strooper\\
  Head of School\\
  School of Information Technology and Electrical Engineering\\
  The University of Queensland\\
  St Lucia, Q 4072\\
  \bigskip\bigskip
  Dear Professor Strooper,
\end{flushleft}

In accordance with the requirements of the degree of Bachelor of
Engineering in the division of 
Electrical Engineering,
Electrical and Biomedical Engineering,
Electrical and Computer Engineering,
Software Engineering,
Mechatronic Engineering,
I present the
following thesis entitled ``Analysing time-stepped neural networks with temporally rich frame-based data''.  This work was performed under the supervision of Prof. Janet Wiles.

I declare that the work submitted in this thesis is my own, except as
acknowledged in the text and footnotes, and has not been previously
submitted for a degree at The University of Queensland or any other
institution.

\begin{flushright}
	Yours sincerely,\\
	\medskip
	\emph{}\\
	\medskip
	Joshua Arnold.
\end{flushright}

\cleardoublepage

% Dedication (if you want it):
\vspace*{70mm}
\begin{center}
\renewcommand{\baselinestretch}{1.0}
\sl
	To \ldots
\end{center}

\chapter{Acknowledgments}

Acknowledge your supervisor, preferably with a few short and specific
statements about his/her contribution to the content and direction of
the project.  If you collaborated with another student, acknowledge
your partner's contribution, including any parts of the thesis of
which s/he was the principal author or co-author; this information can
be duplicated in footnotes to the chapters or sections to which your
partner has contributed.  Briefly describe any assistance that you
received from technical or administrative staff.  Support of family
and friends may also be acknowledged, but avoid sentimentality---or
hide it in the dedication.

\cleardoublepage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    ABSTRACT    %%%%%%%%%%%%%%%%%%%%%%%
\chapter{Abstract}

\begin{itemize}
\item Need to nail down thesis of the thesis... \hfill

\item Linear patterns can be extracted from event-based data represented as a two dimensional temporally decayed images in time-stepped neural network models. \hfill

\end{itemize}

Event-based sensing offers many advantages in the field of artificial vision however few algorithms are able to leverage the data fully. 
This is due to a disparity between traditional frame-based algorithms developed for 2D images and the 3D nature of event-based data. 
A new event-based dataset of linear movement is presented as a benchmark for simple models.
This dataset is then used to evaluate the representational power of 2D temporally blurred images in frame-based neural networks. 
By retaining a time based blur, frame-based networks are able to implicitly encode for temporal information in predictions. 

\tableofcontents

\listoffigures

\listoftables

\cleardoublepage

\mainmatter
% By default, mainmatter has Arabic page-numbering (1,2,...).

\include{intro}             % 3
\include{litreview}         % 12
\include{datacollection}    % 5
\include{preprocess}        % 4 
\include{pilot}             % 4
\include{convolutions}      % 4
\include{attentional}       % 8
%\include{networks}       
%\include{discussion}        
\include{conclusions}       % 4 



%%%%%%%%%%%%%%%     REFERENCES    %%%%%%%%%%%%%%%%%
%\begin{thebibliography}{99}
%\addcontentsline{toc}{chapter}{References}
%\bibitem{lamport} L.~Lamport, \emph{\LaTeX: A Document Preparation
%System}, 2nd ed. (Addison-Wesley, 1994).
%\bibitem{LABEL2} REFERENCE 2
%\bibitem{ETC.} Etc.
%\end{thebibliography}

\bibliographystyle{IEEEtran}
\bibliography{/home/joti/Documents/References/mendeley_bibs/thesis}



%%%%%%%%%%%%%%%%%    APPENDIX    %%%%%%%%%%%%
\appendix
% Chapters after the \appendix command are lettered, not numbered.
\newpage
\mbox{}
\newpage

% \include appendix chapters here.

\include{evolution}
\include{tbnets}

\cleardoublepage


\end{document}
